Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-03-26 main.Rmd
section identifier
illutrative removed, justification corrected and note included in caption for tables

\begin{table}[ht]
\begin{center}
\begin{tabular}{lr@{~}lr@{~}r}
\hline
circular granularity && expression  && period length\\
\hline
minute-of-hour & $C_1$ & $= L_1(z \mod 60)$  & $P_1 = $&$60$ \\
minute-of-day & $C_2$ & $= L_2(z \mod 60*24)$  & $P_2=$&$`r 60*24`$\\
hour-of-day & $C_3$ & $= L_3(\lfloor z/60\rfloor\mod 24)$  & $P_3 =$&$24$ \\
hour-of-week & $C_4$ & $= L_4(\lfloor z/60\rfloor\mod 24*7)$  & $P_4=$&$`r 24*7`$\\
day-of-week & $C_5$ & $= L_5(\lfloor z/24*60\rfloor \mod 7)$  & $P_5=$&$7$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Illustrative circular granularities with bottom granularity "minutes". Circular granularity $C_i$ relates two linear granularities one of which groups periodically into the other with regular mapping and $P_i$ represents the period length.}
\label{tab:definitions}
\end{table}

@@

\begin{table}[ht]
\begin{center}
\begin{tabular}{lr@{~}lr@{~}r}
\hline
quasi-circular granularity && potential period lengths\\
\hline
$Q_1 =$ day-of-month && $P_1 = 31, 30, 29, 28$\\
$Q_2 =$ hour-of-month && $P_2 = 24*31, 24*30, 24*29, 24*28$\\
$Q_3 =$ day-of-year && $P_3 = 366, 365$\\
$Q_4 =$ week-of-month && $P_4 = 5, 4$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Illustrative quasi-circular granularities $Q_i$ with potential period lengths $P_i$. These quasi-circular granularities relate two linear granularities one of which groups periodically into the other with irregular mapping and hence can not be expressed through modular arithmetic.}
\label{tab:quasi}
\end{table}

@@

```{r tab-mayan}
table_mayan <- tibble(`linear (G)` = c("kin", "uinal", "tun", "katun", "baktun"),
                      `single-order-up cyclic (C)` = c("kin-of-uinal","uinal-of-tun"," tun-of-katun", "katun-of-baktun", 1),
                       `period length/conversion operator (K)`= c(20, 18, 20, 20, 1)) 
kable(table_mayan, 
      format = "latex",
      booktabs = TRUE,
      align = "c",
      caption = "Hierarchy table for Mayan calendar with all circular single-order-up granularities.")
  #row_spec(0, bold = TRUE) %>% 
  #row_spec(1:(nrow(table_mayan)-1), hline_after = T) %>% kable_styling(latex_options = "striped")
```

@@

kable(table_greg, 
      format = "latex",
      booktabs = TRUE,
      caption = "Illustrative hierarchy table for Gregorian calendar with both circular and quasi-circular single-order-up granularities.") %>% 
  #row_spec(0, bold = TRUE) %>%
   kable_styling()
```

@@

### Harmonies and Clashes {#sec:synergy}

@@

### Summarizing the measured variable {#sec:summarize-measured}

@@

  knitr::kable(smart_harmony,
               format = "latex",
               booktabs = TRUE,
                caption = "Harmonies with two cyclic granularity one placed on facet and the other on x-axis.") %>% 
    #row_spec(0, bold = TRUE) %>% 
    kable_styling() %>% 
     add_footnote("NOTE: Out of 30 possible combinations of cyclic granularities, only these 13 are harmony pairs.",
                  notation="none")
```

>>>>

\begin{table}[ht]
\begin{center}
\begin{tabular}{lr@{~}lr@{~}r}
\hline
circular granularity && expression  && period length\\
\hline
minute-of-hour & $C_1$ & $= L_1(z \mod 60)$  & $P_1 = $&$60$ \\
minute-of-day & $C_2$ & $= L_2(z \mod 60*24)$  & $P_2=$&$`r 60*24`$\\
hour-of-day & $C_3$ & $= L_3(\lfloor z/60\rfloor\mod 24)$  & $P_3 =$&$24$ \\
hour-of-week & $C_4$ & $= L_4(\lfloor z/60\rfloor\mod 24*7)$  & $P_4=$&$`r 24*7`$\\
day-of-week & $C_5$ & $= L_5(\lfloor z/24*60\rfloor \mod 7)$  & $P_5=$&$7$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Examples of circular granularities with bottom granularity minutes. Circular granularity $C_i$ relates two linear granularities one of which groups periodically into the other with regular mapping and $P_i$ represents the period length.}
\label{tab:definitions}
\end{table}

@@

\begin{table}[ht]
\begin{center}
\begin{tabular}{lr@{~}lr@{~}r}
\hline
quasi-circular granularity && potential period lengths\\
\hline
$Q_1 =$ day-of-month && $P_1 = 31, 30, 29, 28$\\
$Q_2 =$ hour-of-month && $P_2 = 24*31, 24*30, 24*29, 24*28$\\
$Q_3 =$ day-of-year && $P_3 = 366, 365$\\
$Q_4 =$ week-of-month && $P_4 = 5, 4$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Examples of quasi-circular granularities $Q_i$ with potential period lengths $P_i$. These quasi-circular granularities relate two linear granularities one of which groups periodically into the other with irregular mapping and hence can not be expressed through modular arithmetic.}
\label{tab:quasi}
\end{table}

@@

```{r tab-mayan}
table_mayan <- tibble(`linear (G)` = c("kin", "uinal", "tun", "katun", "baktun"),
                      `single-order-up cyclic (C)` = c("kin-of-uinal","uinal-of-tun"," tun-of-katun", "katun-of-baktun", 1),
                       `period length/conversion operator (K)`= c(20, 18, 20, 20, 1)) 
kable(table_mayan, 
      format = "latex",
      booktabs = TRUE,
      caption = "Hierarchy table for Mayan calendar with all circular single-order-up granularities.") %>% 
  kable_styling()
  #row_spec(0, bold = TRUE) %>% 
  #row_spec(1:(nrow(table_mayan)-1), hline_after = T)   
```

@@

kable(table_greg, 
      format = "latex",
      booktabs = TRUE,
      caption = "Hierarchy table for Gregorian calendar with both circular and quasi-circular single-order-up granularities.") %>% 
  #row_spec(0, bold = TRUE) %>%
   kable_styling()
```

@@

## Harmonies and Clashes {#sec:synergy}

@@

## Summarizing the measured variable {#sec:summarize-measured}

@@

  knitr::kable(smart_harmony,
               format = "latex",
               booktabs = TRUE,
                caption = "Harmonies with two cyclic granularity one placed on facet and the other on x-axis. Out of 30 possible combinations of cyclic granularities, only these 13 are harmony pairs.") %>% 
    #row_spec(0, bold = TRUE) %>% 
    kable_styling()
```
